MINOS Handover Plots

### 2024-02-09 minos/validation/handovers.Rmd
Changed some prediction function arguments in r_utils and updated the function calls in modules. Also commented out most spaghetti plots for handovers speed

```{r}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income)

income.spag <- rbind(raw.inc, base.inc)

density_ridges(income.spag, 'hh_income',
               save=shall.we.save, 
               save.path=save.path)

pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
spaghetti_plot(income.spag.sample, 'hh_income',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

rm(raw.inc, base.inc, income.spag)
```

@@

```{r}
raw.nut <- raw.dat %>%
  select(pidp, age, time, ncigs)
base.nut <- base.dat %>%
  select(pidp, age, time, ncigs)

nut.spag <- rbind(raw.nut, base.nut)

spaghetti_plot(nut.spag, 'ncigs',
               save = shall.we.save,
               save.path = save.path)

density_ridges(nut.spag, "ncigs",
               save = FALSE,
               save.path = save.path)

rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, matdep) %>%
  filter(!matdep %in% miss.values)
base.s <- base.dat %>%
  select(pidp, age, time, matdep) %>%
  filter(!matdep %in% miss.values)

spaghetti_plot(spag, 'matdep',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, chron_disease) %>%
  filter(!chron_disease %in% miss.values)
base.s <- base.dat %>%
  select(pidp, age, time, chron_disease) %>%
  filter(!chron_disease %in% miss.values)

spag$chron_disease <- as.numeric(spag$chron_disease)

spaghetti_plot(spag, 'chron_disease',
               save = shall.we.save,
               save.path = save.path)

density_ridges(spag, 'chron_disease',
               save=shall.we.save, 
               save.path=save.path)

pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
spaghetti_plot(spag.sample, 'chron_disease',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, hourly_wage)
base.s <- base.dat %>%
  select(pidp, age, time, hourly_wage)

spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)

# now a version limited to 0-100
spag <- spag %>%
  filter(hourly_wage <= 300)
spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)

```{r}
# some basic statistics about hourly_wage variable
print("Some basic statistics on hourly_wage. These are all for 2020.")
raw.2020 <- raw.dat %>% filter(time == 2020)
print('All living people in 2020')
print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
# number individuals with an hourly_wage > 0
print('People not in work')
print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))

# Number in work
print('People in work')
print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))

# Extreme hourly_wage values
print('Extreme hourly wage values: HIGH')
print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))

raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
print('Extreme hourly wage values: LOW (non-zero)')
print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
```

>>>>

```{r}
# raw.inc <- raw.dat %>%
#   select(pidp, age, time, hh_income)
# base.inc <- base.dat %>%
#   select(pidp, age, time, hh_income)
# 
# income.spag <- rbind(raw.inc, base.inc)
# 
# density_ridges(income.spag, 'hh_income',
#                save=shall.we.save, 
#                save.path=save.path)
# 
# pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
# income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
# spaghetti_plot(income.spag.sample, 'hh_income',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.inc, base.inc, income.spag)
```

@@

```{r}
# raw.nut <- raw.dat %>%
#   select(pidp, age, time, ncigs)
# base.nut <- base.dat %>%
#   select(pidp, age, time, ncigs)
# 
# nut.spag <- rbind(raw.nut, base.nut)
# 
# spaghetti_plot(nut.spag, 'ncigs',
#                save = shall.we.save,
#                save.path = save.path)
# 
# 
# density_ridges(nut.spag, "ncigs",
#                save = FALSE,
#                save.path = save.path)
# 
# rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, matdep) %>%
#   filter(!matdep %in% miss.values)
# base.s <- base.dat %>%
#   select(pidp, age, time, matdep) %>%
#   filter(!matdep %in% miss.values)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'matdep',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, chron_disease) %>%
#   filter(!chron_disease %in% miss.values)
# base.s <- base.dat %>%
#   select(pidp, age, time, chron_disease) %>%
#   filter(!chron_disease %in% miss.values)
# 
# spag <- rbind(raw.s, base.s)
# 
# spag$chron_disease <- as.numeric(spag$chron_disease)
# 
# spaghetti_plot(spag, 'chron_disease',
#                save = shall.we.save,
#                save.path = save.path)
# 
# density_ridges(spag, 'chron_disease',
#                save=shall.we.save, 
#                save.path=save.path)
# 
# pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
# spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
# spaghetti_plot(spag.sample, 'chron_disease',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, hourly_wage)
# base.s <- base.dat %>%
#   select(pidp, age, time, hourly_wage)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'hourly_wage',
#                save = shall.we.save,
#                save.path = save.path)
# 
# # now a version limited to 0-100
# spag <- spag %>%
#   filter(hourly_wage <= 300)
# spaghetti_plot(spag, 'hourly_wage',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

```{r}
# # some basic statistics about hourly_wage variable
# print("Some basic statistics on hourly_wage. These are all for 2020.")
# raw.2020 <- raw.dat %>% filter(time == 2020)
# print('All living people in 2020')
# print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
# # number individuals with an hourly_wage > 0
# print('People not in work')
# print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
# print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
# 
# # Number in work
# print('People in work')
# print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
# print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
# 
# # Extreme hourly_wage values
# print('Extreme hourly wage values: HIGH')
# print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
# print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
# print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
# print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
# print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
# print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
# 
# raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
# print('Extreme hourly wage values: LOW (non-zero)')
# print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
# print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
# print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
# print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
```
